A neural coarse graining theory of consciousness

### 2019-03-24 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

%% ============================== Useful packages ============================= %
\usepackage[dvipsnames,table,xcdraw]{xcolor}
\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{authblk}
\usepackage{float}
\usepackage{tikz}
\usepackage[threshold=2, autopunct=true, autostyle=true]{csquotes}

@@

% Real content
	% Finished part
	% Outline items that can be integrated into main text
		\newenvironment{ants}
			{
			 \begin{easylist}[itemize]
		 	}
			{
			\end{easylist}
			}

	% Writing Materials
		\newenvironment{writingMaterials}
			{
			\begin{tcolorbox}[size=small, colframe=black!20!white, toprule=1mm]
				Writing Materials
			\end{tcolorbox}

			\begin{easylist}[itemize]
			}
			{
			\end{easylist}
			\begin{tcolorbox}[size=small, bottomrule=1mm, halign=flush right, colframe=black!20!white]
				Writing Materials
			\end{tcolorbox}
			}

@@

@@

% ============================================================================ %
%                                    Authors                                   %
% ============================================================================ %
\author[1]{Acer Y.C. Chang\thanks{acercyc@araya.org}}
\author[1]{Martin Biehl\thanks{martin@araya.org}}
\author[1]{Ryota Kanai\thanks{kanair@araya.org }}
\affil[1]{ARAYA, Inc., Tokyo, Japan}

@@

@@

	% ============================================================================ %
	%                                  Out theory                                  %
	% ============================================================================ %
	\section{A neural coarse graining theory of consciousness}
		\ideaBox{Need to describe my intuition more concretely}

		\begin{ants}
			\toWrite{Do I need to start with my philosophical intuition?}

@@

			@ If the new set of variables are informational closured, then this creates a new "reality" for all the variables inside.

			@ Reality means the all the information (include variables and the relationships) within the boundary of causal or informational influence between variables.

@@

		% ----------------------------------------------------------------------------

			%% reasoning

				@ ============= reasoning ============

				@ Information processing in the neural system exists at different level of abstraction.

				@ \idea{okay, I need to be very careful about the causal relation here.}

				@ However, at a macroscopic scale, information processing can achieve non-trivial informational closure (Fig. \ref{fig:CGandIC})

			%% our claim
				@ ============ our claim  ============

				@ We claim that the state of a coarse-grained scale which realises non-trivial informational closured correlates the state of consciousness.

@@

			%% Following
				@ In the following part, we....\todo{todo}

@@

		\begin{figure}[H]
			\includegraphicsTodo[width=\textwidth]{CGandIC.png}
			\caption{informational closure through neural coarse-graining}
			\label{fig:CGandIC}
		\end{figure}

		% ==================================== %
		% Backup
		% ==================================== %
		\begin{ants}

				@@ Oppenheim , P. , \& Putnam , H. ( 1958 ). Unity of science as a working hypothesis . In H. Feigl , G. Maxwell , \& M. Scriven (Eds.), Concepts, theories, and the mind – body problem (pp. 3 – 36 ). Minneapolis : University of Minnesota Press .
				@@ Attneave , F. ( 1961 ). In defense of homunculi . In W. A. Rosenblith (Ed.), Sensory communication (pp. 777 – 782 ). Cambridge, MA : MIT Press .
				@@ Hofstadter , D. R. ( 1979 ). Godel, Escher, Bach, an eternal golden braid . New York : Basic Books .
				@@ Churchland , P. S. , \& Sejnowski , T. J. ( 1992 ). The computational brain . Cambridge, MA : MIT Press .
				@@ Wimsatt , W. C. ( 1994 ). The ontology of complex systems: levels of organization, perspectives, and causal thickets. Canadian Journal of Philosophy , 20 , 207 – 274 .
				@@ Lycan ,  W. G.  ( 1996 ).  Consciousness and experience .  Cambridge, MA :  MIT Press .

			@ It's important that not the neural states but the coarse-grained state determine contents of consciousness.

			@ Consciousness is information
				@@ Information is level-dependent.

				@@ Information is different at microscopic and macroscopic levels

				@@ Consciousness must be level-dependent

				@@ conscious perception are very stable and time invariant.
				@@ Conscious perception is informative but we loss all the precise information about the states at microscopic level.
		\end{ants}
		% ==================================== %

		\subsection{Measure of conscious level}
			\begin{ants}
				@ The level of consciousness can be computed from how much degree of the non-trivial informational closure in a coarse-grained scale.

				@ Based on Equation xxx\todo{equation}, the measure of non-trivial informational closure can be decomposed to XXX and XXX.

				@ use \includegraphics{WritingMaterials/PDFXCview_2018-06-01_17-44-30.png}

				@ or use \includegraphics{WritingMaterials/PDFXCview_2018-06-04_19-18-12.png}

@@

				@ \rewording{Note that, our claim is that informational closure is a more fundamental property that correlates consciousness. A species acquiring advantage to model a complex environment through evolution and , therefore, achieving a high-level non-trivial informational closure has a high level of consciousness, is the consequence of the evolutional process. }

@@

		\subsection{Conscious contents}
			\begin{ants}
				@ We claim that conscious contents correspond to the state of the informational closure.

				@ \idea{= not sure I want to say this here =}

				@ Consciousness is informative. A conscious percept including volition and intention is a unique state that narrowing down all possible states into one. Therefore, a conscious percept reduces a huge amount of uncertainty.

				@ This is the same claim as the third axiom called "information" in IIT. \needref{information axiom and need to say more about this.}

				@ ====================================

				@ Note that because the closure is at a coarse-grained scale one state of the informational closure can be mapped to several states at microscopic scale.
			\end{ants}

		\subsection{Sensory hierarchy and neural coarse-graining
			\critical{This is super important. I need to deal with this very carefully. Need to completely rewording}}\label{sec:SensoryHierarchy}

			\begin{figure}[H]
				\includegraphicsTodo[width=0.8\textwidth]{hierarchy.pdf}
				\caption{Coarse-grain and sensory anatomical hierarchies}
				\label{fig:hierarchy}
			\end{figure}

			\begin{figure}[H]
				\includegraphics[width=\textwidth]{WritingMaterials/SeperationOfCGandCortHierachy.pdf}
%				{Coarse-grain and sensory anatomical hierarchies}
			\end{figure}

			\begin{ants}
				@ It's important to note that the coarse-graining direction is not necessary to be align with anatomical sensory hierarchy in the neural system.

				@ the coarse-grained information is needed and computed only when the information is required for microscopic scale processing.

				@ \toWrite{I need a strong example here}

				@ Of course, from evolutional perspective, neural system should develop a better hardware to support neural coarse-graining

				@ It is possible that the neural system represents higher-level information processing by low level physical subtract. For example, studies have found representation for summery statistics of signal and neural. population.\needref{neural representation for summery statistics}\\
				From this point of view, sensory hierarchy may extend along with levels of coarse-graining.

@@

		\subparagraph{more information theory and philosophy relevance}
			\begin{writingMaterials}
				@ One consequence of coarse-graining is that it makes it permissible to ignore certain causal factors that would be relevant at more fine-grained level of description. \cite{price2007causation}

				@ This means the fine-grain variable does not exist at the coarse-grained causal chain.
			\end{writingMaterials}

		% ============================================================================ %
		%                         Information and system theory                        %
		%                                                                              %
		% ============================================================================ %
		\subsection{Information and system theory}
			\idea{A closure can define a system, consciousness is information}

			\idea{Could be linked to system theory, but may need help}

			\rewrite{
				This self-referential distinction from its environment therefore gives rise to the specific autonomy of such a system. Consequently, in systems theory, closure properties and autonomy are considered to be closely related concepts which are both at the heart of defining the system itself.}

		\subsection{Empirical approaches of measuring neural informational closure}

	\section{Conscious vs unconscious processing}
		\ideaBox{Now we can combine "Relation to empirical findings in neuroscience and studies of consciousness" and "About Phenomenology (conscious processing)" in to this}

	\section{Comparison with other theories}
		\ideaBox{Main points should be same/diff, our advantages, and predictions}

		\subsection{Theories about level of abstraction and coarse-graining}
			\begin{ants}
				@ Before the current theory, several theories and perspectives of consciousness have proposed the notion that links level of abstraction or coarse-graining in the neural system to consciousness.

				@ We shortly describe two theories which is \todo{XXX and XXX} related to our current proposal.
			\end{ants}

			\subsubsection{Intermediate Level Theory}
				\begin{ants}
					@ Intermediate Level Theory (ILT) proposes that conscious experience only correlates specific levels of representations in the sensory processing the hierarchy. \citep{prinz2007intermediate, jackendoff1987consciousness}. This theory claims that consciousness only associates with the representation at  intermediate levels rather than the ones at lower-level or higher-level.

					@ A critical difference between ILT and our theory is that our theory doesn't assume the direction of coarse-graining should align with the direction of  anatomical processing levels along cortical hierarchies.
				\end{ants}

				\begin{comment}
					%% Back up materials
					@ \rewrite{
						The intermediate level theory originally proposed by Ray Jackendoff and further defended and specified by Jesse Prinz proposes that within the hierarchy of representations that are used to describe the cognitive system, conscious experience occurs only for specific levels of representation. The theory is rooted in Jackendoff ’s analysis of different cognitive systems such as vision, language, and music and the subsequent observation that consciousness does not arise anywhere within these systems. According to Jackendoff, consciousness is not associated with low-level, nor with high-level representations, but rather with those implying intermediate levels of processing. For instance, in the domain of object recognition, it is assumed that the visual system comprises a low level with local computations of visual features, an intermediate level reflecting binding and object recognition, and a higher level computing viewpoint invariance and representing abstract categories. According to Jackendoff and Prinz, conscious experience is not comprised of a disunified picture of visual features, nor is it represented by viewinvariant categories. Rather it is composed of bound and specific instances of objects that are assumed to be computed at the intermediate level of representation. In an analogous manner, speech perception can be decomposed into three levels: an acoustic representation of speech sounds at the lower level, a high level involving abstract lexical and syntactic categories, and in between a word recognition level relying on phonological representations. This theory explains why the conscious experience associated with speech perception mostly involves phonological representations, rather than other levels of representations. In Jackendoff and Prinz’ theory,the privileged role of the intermediate level of processing is based on the need for real-time computational efficiency. Indeed, this level of representation is assumed to be the most relevant one regarding ecological and functional needs. Another important aspect of this theory concerns the central role of attention during conscious experience. Here, attention is defined as a selection process that acts as a gate to working memory mechanisms. It performs the function of selecting the relevant information that is amplified afterward and then becomes conscious. Indeed, Prinz acknowledges that activation of an intermediatelevel representation on its own cannot be a sufficient condition for consciousness, given that those representations can be activated during subliminal perception. However, this theory makes the crucial postulate that the amplification of intermediatelevel representations by attention is a necessary and sufficient condition for consciousness. In sum, for each domain of processing, the content of consciousness at a particular moment is supported by a representational structure of intermediate level for that domain, which is selected to enter short-term memory, and enriched by attentional processing.} \cite{banks2009encyclopedia}

@@

					@ about why it is this level
					@@ \rewrite{
						Under the computational interpretation, the “why” question means: In what sense are intermediate level representations computationally important or distinctive? Th is is a tractable question, and it may lead to insights into the function of consciousness. Representations at the intermediate level are ideally suited for real- time deliberative behavioral responses. Low- level representations fail to bind features into coherent wholes. If we are going to interact with our environment, the low level is not a good guide. Th e high level is a good deal better for action, but also suboptimal. Th e high level tells us the category of the stimuli we perceive, but from an allocentric point of view. It abstracts away from stimulus features that are crucial for action. If we encounter a predator, the high- level visual representation does not tell us if it is facing toward us or away from us. Without that knowledge, we cannot decide what course of action to take. So, I propose that the intermediate level plays a distinctive role in information processing. It delivers representations that are coherent but viewpoint specifi c. Th ese representations are useful for determining what to do here and now.arg1} \cite{prinz2007intermediate}
					@@ \rewrite{
						I conclude that the intermediate level plays a distinctive and important computational role. Some researchers fi nd this puzzling. In wondering why the intermediate level is privileged, they note the arbitrariness of the fact that perceptual hierarchies have three levels. Could they not have two? Or a hundred? Do the 50 or so areas that contribute to visual processing really divide neatly into three levels? I think these puzzles depend on a particular understanding of what the word “intermediate” amounts to. One might get caught up in the fact that the intermediate level is the second stage in a sequence. Call this the “serial understanding of the intermediate level.” Alternatively, one might think of the intermediate level semantically. On this reading, the intermediate level is one that is not abstract and categorical, but not piecemeal or disunifi ed. Th ese notions are all in need of some refi nement, but, as a fi rst approximation, the idea is that intermediate- level representations are neither too specifi c nor too general.}\cite{prinz2007intermediate}

					%% Our theory
					@ However, as we mentioned in Section \ref{sec:SensoryHierarchy}, \rewrite{The notion of ‘ levels ’ deployed here is functional and very different from that of successive anatomical processing stages along cortical hierarchies [75] or from anatomic scales in the brain. The multi-level concept in [2] is more akin to Marr ’ s original distinction between the levels of (neural) implementation, algorithms, and computational theory [122], but focuses on how conscious representations correspond to computational operations at levels with lower complexity and representational capacity.}
				\end{comment}

>>>>

%% ============================== Useful packages ============================= %
\usepackage[dvipsnames,table,xcdraw]{xcolor}
\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{authblk}
\usepackage{float}
\usepackage{tikz}

@@

% Real content
	% Outline items that can be integrated into main text
		\newenvironment{ants}
			{
			 \begin{easylist}[itemize]
		 	}
			{
			\end{easylist}
			} %

	% Writing Materials
\newenvironment{writingMaterials} %
	{
	\begin{tcolorbox}[size=small, colframe=black!20!white, toprule=1mm]
		Writing Materials
	\end{tcolorbox}
	\begin{easylist}[itemize]
	}
	{
	\end{easylist}
	\begin{tcolorbox}[size=small, bottomrule=1mm, halign=flush right, colframe=black!20!white]
		Writing Materials
	\end{tcolorbox}
	}

@@

% review loop annotation
    \usepackage[xcolor, outerbars]{changebar}
    \cbcolor{red}

    % start anchor: \rlstart
    \newcommand{\rlstart}[1]{  %
        \setlength\changebarwidth{#1pt*2}  %
        \hspace*{-40pt}
        \cbstart{\textcolor{red}{\newline\textbf{iteration #1}}\newline}}

    % end anchor: \rlend
    \newcommand{\rlend}{\cbend}

% quote
\newcommand{\myQuote}[1]{\textit{``#1''}}

@@

% ============================================================================ %
%                                    Authors                                   %
% ============================================================================ %
\author[1]{Acer Y.C. Chang\thanks{acercyc@araya.org}}
\author[1]{Martin Biehl\thanks{martin@araya.org}}
\author[1]{Yen Yu\thanks{martin@araya.org}}
\author[1]{Ryota Kanai\thanks{kanair@araya.org }}
\affil[1]{ARAYA, Inc., Tokyo, Japan}

@@

		% information-based claim 
		Our theory takes a strong assumption that consciousness is information-based, information correlates of consciousness (ICC)\todo{Complete this argument}

@@

	\section{A neural coarse graining theory of consciousness}

\rlstart{3}
        In this section, we formally introduce our theory \tnamefull \todo{We need a good name}.

        We starts our argument from a presumptive fact that every human conscious precept is ex trimly informative. Our conscious experience always consists of high multidimensional information involved multiple modalities. Considering information as resolved uncertainty, every conscious percept rules out enormous other possible conscious states in the state space, therefore, gives huge amount of of information. This notion is similar to one of the axiom, \textit{information}, in Integrated Information Theory (IIT 3.0, \cite{oizumi2014phenomenology}) which claims that \myQuote{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...} \citep[p. 2]{oizumi2014phenomenology}.

        Based on this presumptive fact, we further take a radical standpoint and postulate that consciousness fundamentally associate with information in the physical reality (information correlates of consciousness, \cite{chalmers1996conscious, tononi2004information, gamez2011information}) rather than neuronal states (neural correlates of consciousness). That is, consciousness should be information-based. The amount of information comprising a conscious percept should be equivalent to information we can obtain from a specific physical event.

        Nevertheless, even though information involved in every conscious percept is extremely rich, it is still bounded, i.e. boundary exists. Presuming consciousness is information-based, we can deal with the boundary problem \cite{goff2006experiences} by information closure. Additionally, our conscious experience contains not merely trivial informational rather it always provides rich information about the environmental and our bodily states. Therefore, we argue that NTIC is the core entity \highlightAndComment{responsible}{Help me to think of a better term} for consciousness.

        @ As we mentioned in Chapter 3, to form non-trivial informational closure has a huge evolutionary advantage for the creatures interacting with the environment at our scale.

        @ Therefore, NTIC emerges from evolutionary processes is functionally plausible.

        @ Importantly, at the microscopic level, it is impossible to achieve NTIC as we mentioned in chapter 2.

		@ However, at a macroscopic scale, information processing can achieve non-trivial informational closure (Fig. \ref{fig:LevelOfConsciousness})

        @ Therefore, the NTIC correlating conscious experience must settled at coarse-grained macroscopic levels.

@@

        @ information is scale-dependent

		@ If the new set of variables are informational closure, then this creates a new \textit{reality} for all the variables inside.        
		@ \textit{Reality} here means that the all the future states of the system are driven by the current information (include variables and the relationships) within the boundary.

        @

        @ Relationship between coarse-graining, scale and interaction with environment

			@@ conscious perception are very stable and time invariant.
			@@ Conscious perception is informative but we loss all the precise information about the states at microscopic level.

        @ To summaries, in our framework, consciousness is 
			    @@ Intrinsic

			    @@ Informative

				@@ scale-dependent

        % our claim   
			@ We claim that the state of a coarse-grained scale which realises non-trivial informational closured correlates the state of consciousness.

		% Following
			@ In the following part, we....\todo{todo}

@@

@@

				@@ Oppenheim , P. , \& Putnam , H. ( 1958 ). Unity of science as a working hypothesis . In H. Feigl , G. Maxwell , \& M. Scriven (Eds.), Concepts, theories, and the mind – body problem (pp. 3 – 36 ). Minneapolis : University of Minnesota Press .
				@@ Attneave , F. ( 1961 ). In defense of homunculi . In W. A. Rosenblith (Ed.), Sensory communication (pp. 777 – 782 ). Cambridge, MA : MIT Press .
				@@ Hofstadter , D. R. ( 1979 ). Godel, Escher, Bach, an eternal golden braid . New York : Basic Books .
				@@ Churchland , P. S. , \& Sejnowski , T. J. ( 1992 ). The computational brain . Cambridge, MA : MIT Press .
				@@ Wimsatt , W. C. ( 1994 ). The ontology of complex systems: levels of organization, perspectives, and causal thickets. Canadian Journal of Philosophy , 20 , 207 – 274 .
				@@ Lycan ,  W. G.  ( 1996 ).  Consciousness and experience .  Cambridge, MA :  MIT Press
			@ It's important that not the neural states but the coarse-grained state determine contents of consciousness.

\rlend

\rlstart{3}
		\subsection{Measure of consciousness/information correlate of consciousness}

			\begin{ants}
			@ In this thesis, we postulate that NTIC is the core entity of information correlate of consciousness.

			@ We further propose properties of consciousness correlate properties of NTIC

			quantitative hypotheses of conscious level and conscious content.

			@ We first hypothesise that, at time $t$, levels of consciousness $C_{t}^{Level}$ corresponds to the degree of NTIC at coarse-grained levels $NTIC_{t}$.

				\begin{equation}\label{eq:cLevel}
					C_{t}^{Level} = NTIC_{t}
				\end{equation}

			@ We second hypothesise that, the content of consciousness corresponds to the state of the NTIC process.
				\begin{equation}\label{eq:cContent}
					C_{t}^{Content} = Y_{t}
				\end{equation}

			@ We discuss the implications of the two hypotheses in the following. 					
			\end{ants}
			`

			\subsubsection{Level of Consciousness correlates degrees of NTIC of a process}
    			\begin{ants}
    			@ Several key insights about the conscious level can be derived from our theory.

    			@ Equation \ref{eq:nticObjective} implies that conscious level positive correlates the complexity of the environment that the NTIC process encoded.

    			@ This implies that an agent who forms an NTIC process to lives and adapt to a more complex environment should have a higher conscious level than another agent who lives in an environment with more simple dynamics.

    			@ Channel capacity between the current state and the future state of the NTIC process also determines the level of consciousness.

    			@ \todo{Need an example here} A small creatures may live in a simple environment and forms a NTIC process. The predictive information for the next state of the process may be very low. It has consciousness but the levels of consciousness is low.

    			@ Another implication about levels of consciousness from Equation \ref{eq:nticObjective} predictability of the system future state given the current state is crucial for the conscious level. This indicates that the if the system dynamics are highly scholastic and much unpredictable, the conscious level should be low. This notion explicitly indicates that information processed at neuronal scales which encounter heavy noise and are highly scholastic cannot form high level of consciousness.

    			@ Similarly, at macro-scales, if coarse-graining causes coarse-grained macro-variable lose predictive fine-grain information, the predictability become low and also the channel capacity between the current state and future state becomes very small, NTIC would be low as well. K

    			@ \todo{modify this figure}

    				\begin{figure}[H]				\includegraphics[width=\textwidth]{WritingMaterials/FoxitReader_2019-01-31_19-03-59.png}
    				\label{fig:LevelOfConsciousness}
    				\caption{Level of coarse-graining and level of consciousness. The degree of NTIC is not a monotonic function of coarse-graining levels, suggesting that high conscious level may exist at a certain coarse-grained level }
    				\end{figure}

    			@ This non-monotonic relationship bwetween the level of coarse-graining in the neural system and the degree of NTIC explains why only information processed at a certain level can become conscious contents.

@@

    		\subsubsection{Coarse-graining states correlates conscious contents}
    			\begin{ants}
				@ We claim that conscious contents correspond to the state of the NTIC process.

				@ This implies that the complexity of conscious contents is determined by the amount of information encompassed in the NTIC process.

				@ Therefore, larger state space of the NTIC process has, richer  experience the process can be conscious of (e.g., a NTIC process with high dimensionality).

				@ Crucially, even experience of darkness is rich because it rules out other enormous potential state that the NTIC process can be in. Equivalently, knowing the state of the NTIC process when the process experiences darkness also mean acquisition of information of the system.\todo{bad wording}

    			@ This is similar to the the \textit{Information} axiom in integrated information theory which claims that \myQuote{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...} \citep[p. 2]{oizumi2014phenomenology}

    			@ \todo{Need an example here} Follow the example in the last section, a small creatures may live in a simple environment and forms a NTIC process. The predictive information for the next state of the process may be very low. This also implies the richness of the conscious experience this agent has is very limited.

    			@ Our theory naturally explains why consciousness is compositional, because the joint states of entities in the NTIC process determine the contents of consciousness. \ideaCallout{think about it}

				@ Importantly, note that because the closure is at a coarse-grained scale one state of the informational closure can be mapped to several states at microscopic scale.

				@ This supports multiple realisation thesis \needref{multiple realisation} which suggests same conscious experiences can be mapped to different physical implementations.

	    \subsubsection{Reconcile level and content of consciousness}
	        \begin{ants}
	            @ Our theory link conscious level and conscious content together via the state space of the NTIC process.

	            @ When the information encapsulate in the NTIC process is large and reaches a high NTIC, based on our definition, the system has high level of consciousness. Simultaneously, this provides a rich state space which is equivalent to encoding rich predictive environmental dynamic in the system.

	            @ levels and contents of consciousness are just two different measures of a NTIC process.

	            @ this indicates an important prediction in which the conscious level is determined by states that the NTIC process potentially can reach rather the current state of a system.

	            @ For example, some neural states may map to simple sensory experience, e.g. visual experience in a dark room. However, this does not degrade the conscious level. This experience still provides a huge amount of information because it excludes enormous possibilities of visual experience and decrease a large amount of uncertainty.

    			@ Therefore, this framework well integrates the two key but debated concepts in consciousness research \citep{laureys2005neural, bayne2016there}.

				@ \rewording{Note that, our claim is that informational closure is a more fundamental property that correlates consciousness. A species acquiring advantage to model a complex environment through evolution and , therefore, achieving a high-level non-trivial informational closure has a high level of consciousness, is the consequence of the evolution process. }

			\begin{writingMaterials}
    			@ This implies that, based on the Equation \ref{eq:nticObjective}, the self-predictive information about the future states that the current state holds and the information about the environment encoded in the process determine the level of consciousness.

    			@ This also suggests that the richness of the environment being modelled by the			NTIC process has a direct contribution to the level of consciousness.

@@

\rlend

\rlstart{1}
		\subsection{sensory hierarchy and neural coarse-graining}\label{sec:SensoryHierarchy}

			\begin{figure}[H]
				\includegraphics[width=\textwidth]{WritingMaterials/SeperationOfCGandCortHierachy.pdf}
				\label{fig:hierarchy}
			\end{figure}

			\begin{ants}
				@ It's important to note that the coarse-graining direction is not necessary to be align with \critical{Just saying anatomical is not enough. Need better expression} anatomical sensory hierarchy in the neural system.

				@ the coarse-grained information is needed and computed only when the information is required for microscopic scale processing (readout).

				@ Therefore, our theory is very different from consciousness theories focus on the anatomical hierarchy, for example the intermediate Level Theory \citep[see also \ref{IntermediateLevelTheory}]{prinz2007intermediate, jackendoff1987consciousness}.

				@ The truth is that due to the pervasive noise in the microscopic levels in the neural system reliable information processes need to be built upon the coarse-grained levels.

				@ Nevertheless, to exercise causal power in actuators and environments, to read out information at coarse-grained levels is necessary.

				@ In figure \ref{fig:hierarchy}, the blue arrows indicate the readout mechanisms implemented in the neural system.

				@ We argue that the neural correlates of consciousness may not be the fundamental principles for consciousness. The data may contaminate the understanding of consciousness. 
			\end{ants}

            \begin{writingMaterials}
    			@ Of course, from evolutionary perspective, neural system should develop a better hardware to support neural coarse-graining

				@ It is possible that the neural system represents higher-level information processing by low level physical subtract. For example, studies have found representation for summery statistics of signal and neural. population.\needref{neural representation for summery statistics}\\
				From this point of view, sensory hierarchy may extend along with levels of coarse-graining.
            \end{writingMaterials}
\rlend

        \subsection{About boundary}
            \begin{ants}
                @ boundary is fluid 
            \end{ants}

\rlstart{1}
	\section{Conscious versus unconscious processing}
		\ideaBox{Now we can combine "Relation to empirical findings in neuroscience and studies of consciousness" and "About Phenomenology (conscious processing)" in to this}

		\begin{ants}
		    @ Our theory indicates that conscious information needs to fulfil two necessary conditions.

		    @ 1. The information is processed at a certain coarse-grained

		    @ 2. encoded in the NTIC process

		    @ Based on the two conditions, we can classify brain processes into conscious and unconscious processing based on the two conditions.

@@

		\subsection{Conscious Processing}
		    \begin{ants}
		        @ To achieve high NTIC has evolutionary advantage.

		        @ The current state of the process contains the information about its future state. Therefore, the neural system can build forward models to predict the future state of the environment using the information encoded in the NTIC process.

		        @ Cognitive functions recruiting forward models built upon it are conscious. (E.g., planning, imagination, dreaming)
		    \end{ants}

		\subsection{Unconscious Processing}
		    \begin{ants}
    		    @ When processes fail to satisfy either of the two conditions, they remain unconscious.

    		    @ When processes do not meet the first condition, i.e. the information processed not at the certain coarse-grained level, the information will not be included in conscious contents.

    		    @ For example, we are never conscious of neural spike activities at microscopic levels (e.g. single cell activities) because information passing among individual neurons are not at the certain coarse-grained level.

    		    @ Libet's free will experiment can be also explained by our theory.

    		    @ The random neural fluctuation under Libet's free will experiment happens at the microscopic scale \citep{SchurgerE2904}.

    		    @ When processes do not meet the second condition, i.e. processes which do not achieve high NTIC will remain unconscious.

    		    @ This can explain why many "policy-based" processes are not conscious.

    		    @ Policy-based here features those processes taking sensory information as input and directly outputting actions. Therefore, the future states of policy-based processes largely depend on the environmental states and failed to achieve informational closure.

    		    @ Several neural processes are included in this category, e.g. reflexive neural circuit, blindsight, procedure memory. 
		    \end{ants}

        \subsection*{}
            \begin{ants}
                @ To summarise, our theory can well explain the various findings with parsimonious assumptions. 
            \end{ants}

\rlend

	\section{Comparison with other theories}
		\ideaBox{Main points should be same/diff, our advantages, and predictions}
		\begin{ants}
		    @ In this section, we will discuss the relationship between our theory and other popular modern theories of consciousness. 
		\end{ants}

\rlstart{1}
		\subsection{Theories about multilevel views on consciousness and cognition}
			\begin{ants}
			    @ Previously, multilevel views on consciousness and cognition have been proposed.

			    @ In the following, we discussed the differences between our theory and other theories about multilevel views.

@@

			\begin{writingMaterials}
			    @ LEVELS OF ORGANIZATION \cite{wimsatt1994ontology}

			    @ As mentioned previously, the level of coarse-graining is different from the anatomical level.

			    @ \ideaBox{Should I also deal with Marr's level of abstraction?}

			    @ See the discussion in \cite{pennartz2015brain}. But Pennartz focus more on multimodal representation as the most important factor.

			    @ Our proposal is inline with Pennartz's Neurorepresentational theory (Neurorepresentationalism). \cite{pennartz2018consciousness,pennartz2015brain}.

			    @ Some theories also address the relationship between level of processing and consciousness.

			    @ However, it’s crucial to note that our theory claims only the level of coarsegraining achieving NTIC matters to connsciousness rather than the anatomical level of sensory hierarchy

				@ We shortly describe two theories which is \todo{XXX and XXX} related to our current proposal.			    
			\end{writingMaterials}

			\subsubsection{Intermediate Level Theory} \label{IntermediateLevelTheory}
				\begin{ants}
				@ Intermediate Level Theory (ILT) proposes that conscious experience only correlates specific levels of representations in the sensory processing the hierarchy. This theory claims that consciousness only associates with the representation at  intermediate levels rather than the ones at lower-level or higher-level.

				@ As mentioned previously, a critical difference between ILT and our theory is that our theory doesn't assume the direction of coarse-graining should align with the direction of anatomical processing levels along cortical hierarchies (see fig \ref{fig:hierarchy}).
				\end{ants}

			\subsubsection{Pennartz's neurorepresentational theory (Neurorepresentationalism)}
			    \begin{ants}
			    @ Our theory shares some similar concepts with Pennartz's Neurorepresentationalism.

		        @ However, Neurorepresentationalism focuses on multimodal representation.

		        @ Neurorepresentationalism also focuses on "making sense" between representation

		        @ We focus on informational closure which suggests the closure of causal interaction in a system.

		        @ We don't assume any functional properties as the criteria of consciousness. Instead, we propose information as a more fundamental principle correlates consciousness.  
			    \end{ants}

				\begin{writingMaterials}
					%% Back up materials

					@ Prinz suggested that \rewrite{as. Cells in V1 are not promising candidates, because they do not reliably respond in ways that are consistent with features that we experience consciously. } \cite{prinz2007inter    mediate}

				    @ Our prediction is, if information that is carried by v1 neurons are necessary to complete informational closure, the states of V1 neurons should also co-vary with conscious contents.

					@ \rewrite{
						The intermediate level theory originally proposed by Ray Jackendoff and further defended and specified by Jesse Prinz proposes that within the hierarchy of representations that are used to describe the cognitive system, conscious experience occurs only for specific levels of representation. The theory is rooted in Jackendoff ’s analysis of different cognitive systems such as vision, language, and music and the subsequent observation that consciousness does not arise anywhere within these systems. According to Jackendoff, consciousness is not associated with low-level, nor with high-level representations, but rather with those implying intermediate levels of processing. For instance, in the domain of object recognition, it is assumed that the visual system comprises a low level with local computations of visual features, an intermediate level reflecting binding and object recognition, and a higher level computing viewpoint invariance and representing abstract categories. According to Jackendoff and Prinz, conscious experience is not comprised of a disunified picture of visual features, nor is it represented by viewinvariant categories. Rather it is composed of bound and specific instances of objects that are assumed to be computed at the intermediate level of representation. In an analogous manner, speech perception can be decomposed into three levels: an acoustic representation of speech sounds at the lower level, a high level involving abstract lexical and syntactic categories, and in between a word recognition level relying on phonological representations. This theory explains why the conscious experience associated with speech perception mostly involves phonological representations, rather than other levels of representations. In Jackendoff and Prinz’ theory,the privileged role of the intermediate level of processing is based on the need for real-time computational efficiency. Indeed, this level of representation is assumed to be the most relevant one regarding ecological and functional needs. Another important aspect of this theory concerns the central role of attention during conscious experience. Here, attention is defined as a selection process that acts as a gate to working memory mechanisms. It performs the function of selecting the relevant information that is amplified afterward and then becomes conscious. Indeed, Prinz acknowledges that activation of an intermediatelevel representation on its own cannot be a sufficient condition for consciousness, given that those representations can be activated during subliminal perception. However, this theory makes the crucial postulate that the amplification of intermediatelevel representations by attention is a necessary and sufficient condition for consciousness. In sum, for each domain of processing, the content of consciousness at a particular moment is supported by a representational structure of intermediate level for that domain, which is selected to enter short-term memory, and enriched by attentional processing.} \cite{banks2009encyclopedia}

@@

					@ about why it is this level
					@@ \rewrite{
						Under the computational interpretation, the “why” question means: In what sense are intermediate level representations computationally important or distinctive? Th is is a tractable question, and it may lead to insights into the function of consciousness. Representations at the intermediate level are ideally suited for real- time deliberative behavioral responses. Low- level representations fail to bind features into coherent wholes. If we are going to interact with our environment, the low level is not a good guide. Th e high level is a good deal better for action, but also suboptimal. Th e high level tells us the category of the stimuli we perceive, but from an allocentric point of view. It abstracts away from stimulus features that are crucial for action. If we encounter a predator, the high- level visual representation does not tell us if it is facing toward us or away from us. Without that knowledge, we cannot decide what course of action to take. So, I propose that the intermediate level plays a distinctive role in information processing. It delivers representations that are coherent but viewpoint specifi c. Th ese representations are useful for determining what to do here and now.arg1} \cite{prinz2007intermediate}
					@@ \rewrite{
						I conclude that the intermediate level plays a distinctive and important computational role. Some researchers find this puzzling. In wondering why the intermediate level is privileged, they note the arbitrariness of the fact that perceptual hierarchies have three levels. Could they not have two? Or a hundred? Do the 50 or so areas that contribute to visual processing really divide neatly into three levels? I think these puzzles depend on a particular understanding of what the word “intermediate” amounts to. One might get caught up in the fact that the intermediate level is the second stage in a sequence. Call this the “serial understanding of the intermediate level.” Alternatively, one might think of the intermediate level semantically. On this reading, the intermediate level is one that is not abstract and categorical, but not piecemeal or disunifi ed. Th ese notions are all in need of some refi nement, but, as a fi rst approximation, the idea is that intermediate- level representations are neither too specifi c nor too general.}\cite{prinz2007intermediate}

					%% Our theory
					@ However, as we mentioned in Section \ref{sec:SensoryHierarchy}, \rewrite{The notion of ‘ levels ’ deployed here is functional and very different from that of successive anatomical processing stages along cortical hierarchies [75] or from anatomic scales in the brain. The multi-level concept in [2] is more akin to Marr ’ s original distinction between the levels of (neural) implementation, algorithms, and computational theory [122], but focuses on how conscious representations correspond to computational operations at levels with lower complexity and representational capacity.}\cite{pennartz2018consciousness,pennartz2015brain}
				\end{writingMaterials}

\rlend

\rlstart{1}	
		\subsection{First-order theories}
